---
title: "Not Simple document"
author: "Robert Ariss"
date: 2026-09-25
output: html_document
---

I'm an R Markdown document! 

# Section 0: libraries

```{r message = F}
library(tidyverse)
```


# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

```{r echo = F, message = F}
plot_df = 
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1+ 2 * x + rnorm(1000),
  )
head(plot_df)
```

# Section 4: a plot

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

# Section 5: learning assessment

```{r}
la_df = 
  tibble(
    la_num = rnorm(500, mean = 1),
    la_fac = la_num > 0,
    la_num_av = abs(la_num)
  )

ggplot(la_df, aes(x = la_num_av)) + geom_histogram()

median_la_num = median(pull(la_df, la_num))
```

The median of the variable containing absolute values is `r round(median_la_num, digits = 2)`

# Section 6: formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell

# Section 7: Learning Assessment 3

* The median is `r round(median(pull(la_df, la_num)), 2)`

* The mean is `r round(mean(pull(la_df, la_num)), 2)`

* The standard deviation is `r round(sd(pull(la_df, la_num)), 2)`

Histogram

```{r}
ggplot(plot_df, aes(x = x)) + geom_histogram()
```

